\documentclass[]{deedy-resume-reversed}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

\namesection{Yejju Sathya Sai}{ %\urlstyle{same}\href{http://example.com}{example.com}| \href{http://example2.co}{example2.co}\\
\href{mailto:john.doe@example.com}{john.doe@example.com} | \href{tel:11111111111}{111.111.1111}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.60\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Company A}
\descript{| Advanced Development Intern }
\location{May 2018 – Aug 2018 | Somewhere, XX}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed a cloud-based solution to automate and enhance the engineering process for network installation using AWS and Python.
\item Worked with other teams to create a system to collect and visualize telemetry data of network elements in real time using AWS, Python, and DOMO.
\item Consulted with other teams to jump start cloud-technology adoption and solutions throughout the company.
\item Contributed to initial planning for optics-alignment system utilizing AWS, reinforcement learning, and an IoT architecture.
\end{tightemize}
\sectionsep

\runsubsection{Company B}
\descript{| Intern }
\location{Feb 2017 – Nov 2017 | Somewhere, XX}
\begin{tightemize}
\item Coordinated with multiple departments to lead a software product evaluation resulting in a fit-for-purpose verdict and provided a recommendation on moving forward.
\item Organized meetings with the vendor to receive in-depth product information and answers to cross-departmental questions.
\item Participated on the Web Development Taskforce to provide AngularJS sites to internal customers.
\item Participated in an internal CodeJam to prototype a blockchain application for managing a model supply-chain.
\item Worked with a team to plan executive visit and team-building exercise for 200 employees.
\end{tightemize}
\sectionsep

\runsubsection{My University ITS}
\descript{| Assistant Support Specialist }
\location{Aug 2015 – Oct 2016 | Somewhere, XX}
\begin{tightemize}
\item Interacted with clients to assess their problems and implement a solution in an efficient, friendly manner.
\item Prepared workstations and laptops for future use by company employees.
\item Created scripts to automate common tasks and increase productivity.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Space Robotics Team}
\descript{| Path-Planning Lead}
\location{Jan 2018 – Present | Somewhere, XX}
\begin{tightemize}
\item Spearhead the development effort for the path-planning functionality of a team of three robots.
\item ROS provides movement servers and the planning is being implemented in Python to allow for fully-autonomous operation.
